---
title: "ggrob_FinalHomeworkCode_02"
author: "Gianna Grob"
date: "9/29/2019"
output: html_document
---

***

# Introduction 

***

This is the code for [Homework 2](https://fuzzyatelin.github.io/bioanth-stats/homework-02.html), on week three of AN597. This homework is associated with [Module 6](https://fuzzyatelin.github.io/bioanth-stats/module-06/module-06.html), [Module 7](https://fuzzyatelin.github.io/bioanth-stats/module-07/module-07.html), and [Module 8](https://fuzzyatelin.github.io/bioanth-stats/module-08/module-08.html#probability_mass_functions).

The information for the question is as follows:

>Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

## Question 1

What is the probability that she will hear more than 8 calls during any given session? 

```{r}
ppois(8, lambda = 15, lower=FALSE) #Find the upper tail for more than 8 calls in a session
```

Hearing 8 or more calls is very likely with a probability of 96.26%.

## Question 2

What is the probability that she will hear no calls in a session?

```{r}
dpois(0, lambda = 15) #Test for 0 calls in a session
```

The chance of hearing 0 calls is very low with an occurance of 3.06e-07.

## Question 3

What is the probability that she will hear exactly 3 calls in a session?

```{r}
dpois(3, lambda = 15) #Find chance of hearing exactly 3 calls.
```

The probability she will hear exactly 3 calls will be 0.00017.

## Question 4

Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.

```{r}
x <- 0:30 #set range of 0 to 30.
l = 15 #Make l our lambda value of 15 calls
probset<-dpois(x=x,lambda=l) #Set probability with our range and lambda values
barplot(probset,names.arg=x,space=0,xlab="x",ylab="Pr(X = x)",main="Probability Mass Function") #Create barplot of the probability mass function as done in Module 8. 
```

## Question 5

Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).

```{r}
rpois(104,15) #Set-up a simulation for 104 results for our lambda value of 15
```

Results will be different every time since it is a simulation, but the above code will simulate 104 results with different amount of calls heard.

## Question 6

Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?

```{r}
x <- rpois(104,15) #Create a vector that is our simulation from above 
hist(x, xlim = c(0,30), main = "Histogram of 104 Simulations", xlab = "Number of Calls", ylab = "Probability", probability = TRUE) #Create histogram with simulation with range from 0 to 30.
```

The main difference between this plot and the plot from Question 4 is the shape of the plot. The plot from Question 4 has a more normal curve, with equal amounts on both sides of the curve, compared to this plot which is more random depending on the simulation.

### Challenges Faced

1) Learning how to do probability problems.
2) Creating a graph for Question 4, not sure if I made the correct one. Just used one off the modules.
3) Creating the histogram. Is the probabilty addition necessary? With and without gives a graph, but they look different. 
